The Evolution of Manufacturing Ecosystem in Cloud Manufacturing Architecture

### 2016-05-25 background.tex
change the background

User is the basic activity unit in the manufacturing ecosystem, the interaction between users will change their \begin{inparaenum}[1)]
\item type,
\item status and 
\item niche width
\end{inparaenum}, 
all these changes contribute to microscopic evolution of the ecosystem. More specifically, type change describes the change of user's type among pure demander, pure provider and complex user; status change describes weather a user in the ecosystem or not; niche width change describes the importance or condition of the user, especially the provider and we will only discuss the provider's niche width in this paper. \autoref{tab:userchange} concludes the appearances that we will study in this paper.

@@

>>>>

User is the basic activity individual in the manufacturing ecosystem, the interaction between users will change their \begin{inparaenum}[1)]
\item type,
\item status and 
\item niche width
\end{inparaenum}, 
all these changes contribute to microscopic evolution of the ecosystem. More specifically, type change describes the change of user's type among pure demander, pure provider and complex user; status change describes weather a user in the ecosystem or not; niche width change describes the importance or condition of the user, especially the provider and we will only discuss the provider's niche width in this paper. \autoref{tab:userchange} concludes the appearances that we will study in this paper.

@@

Individual evolution will lead to the evolution of the whole ecosystem and the overall effect is greater than the sum of these individuals. the amount, diversity, operation pattern recognition and service cycle rate are the topics of macroscopic evolution.
